Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-18 manuscript/manuscript.tex
changed implementation
Some changes

\subsection*{Implementation}
We investigate the performance of approximate betweenness centrality algorithms on the metagenomic graphs to find inter-genome repeats. We used the implementations provided by \textsc{NetworKit}\cite{networkit} library. \textsc{NetworKit} is an open source library for high-performance network analysis. It implements effecient graph algorithms and parallelize most of them. It provides implementation for variety of centrality measures. We used the implementation of approximate betweenness centrality. For our experiments, we use the parallelized implementation for the algorithm by Matteo et al.\cite{matteo} and serial implementation for the algorithm by Geisberger et al.\cite{sanders}.

@@

\section{Results} 
We evaluate the effect of using approximation algorithms for betweenness centrality on finding inter-genome repeats using the simulated datasets described above.
%We use the notion of Sensitivity, specificity, and precision to define the quality of repeat detection.
A good repeat detection strategy should have high sensitivity, specificity, and precision. Sensitivity is the measure of proportion of actual repeats which are correctly identified by the algorithm. Specificity is the proportion of non-repeats correctly identified by the algorithm. Precision is the proportion of repeats identified that are correct. High sensitivity is desired because we want to remove as many repeats from the graph. High specificity is desired because we do not want to remove non-repeats which are incorrectly identified as repeats by algorithm. High precision helps us determine the usefulness of our methods. To calculate sensitivity, specificity, and precision, we define following terms:
\begin{itemize}
\item \textbf{True positives(TP):} Number of nodes marked as a repeat that is found within at least 2 genomes
\item \textbf{False positives(FP):} Number of nodes marked as a repeat that is only found within a single genome
\item \textbf{True negatives(TN):} Number of nodes marked as a non-repeat that is only found within a single genome
\item \textbf{False negatives(FN):} Number of nodes marked as a non-repeat that is found within at least 2 genomes
\end{itemize}

>>>>

\subsection*{Evaluation}
We evaluate the effect of using approximation algorithms for betweenness centrality on finding inter-genome repeats using the simulated datasets described above.
%We use the notion of Sensitivity, specificity, and precision to define the quality of repeat detection.
A good repeat detection strategy should have high sensitivity, specificity, and precision. Sensitivity is the measure of proportion of actual repeats which are correctly identified by the algorithm. Specificity is the proportion of non-repeats correctly identified by the algorithm. Precision is the proportion of repeats identified that are correct. High sensitivity is desired because we want to remove as many repeats from the graph. High specificity is desired because we do not want to remove non-repeats which are incorrectly identified as repeats by algorithm. High precision helps us determine the usefulness of our methods. To calculate sensitivity, specificity, and precision, we define following terms:
\begin{itemize}
\item \textbf{True positives(TP):} Number of nodes marked as a repeat that is found within at least 2 genomes
\item \textbf{False positives(FP):} Number of nodes marked as a repeat that is only found within a single genome
\item \textbf{True negatives(TN):} Number of nodes marked as a non-repeat that is only found within a single genome
\item \textbf{False negatives(FN):} Number of nodes marked as a non-repeat that is found within at least 2 genomes
\end{itemize}

@@

\subsection*{Implementation}
We investigate the performance of approximate betweenness centrality algorithms on the metagenomic graphs to find inter-genome repeats. We carried out experiments on a 64-bit Linux machine with 12 CPUs and 50 GB memory. We used the implementations provided by \textsc{NetworKit}\cite{networkit} library. It implements effecient graph algorithms and parallelize most of them. It provides implementation for variety of centrality measures. We used the implementation of approximate betweenness centrality. For our experiments, we use the parallelized implementation for the algorithm by Matteo et al.\cite{matteo} and serial implementation for the algorithm by Geisberger et al.\cite{sanders}.

\section{Results}
